SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-14 paper/bio.tex
more text

Given the above conditions, the biologists search for VTSs that are
not $k$-connected, i.e., every pair of compartments remain reachable
after dropping $k$ vesicles.\ashu{why asking this question}
\ankit{Maximum connectivity [LGC, Least guarantee connectivity] and minimal connective [LRC (least required connectivity)] (rather than necc and suff cond) required by the graph.}

>>>>

Given the above conditions, the biologists search for VTSs that are
not $k$-connected, i.e., every pair of compartments remain reachable
after dropping $k-1$ vesicles.
%
It has been observed in nature, most VTSs are 3-connected.
%
It raised the natural question what are the properties of VTSs
that are not 3-connected.
%
To study them, we have build a tool that finds VTSs that are not
$k$-connected from some $k$.

\ankit{Maximum connectivity [LGC, Least guarantee connectivity] and minimal connective [LRC (least required connectivity)] (rather than necc and suff cond) required by the graph.}

\input{pm-1-matrix}

\begin{example}
%
In figure~\ref{fig:M1}, we present a VTS that has 3
compartments and 8 molecules, and corresponding pairing matrix that
describes the fusion dependency.
%
Molecules are numbered 0-7.
%
In the VTS, labels consists of sting of molecule ids and overline
over an id indicates that the molecule is active.
%
This VTS is an example of version where every present molecule on
the node is active and activity of the molecules on the
edges are controlled by presence of the other molecules.
%
On the right side of the figure, we present pairing matrix.
%
An entry 1 represents pairing between molecules and
entry $\times$ represents no pairing.
% rectangles colored $\times$ one represents don't cares.
%
Everywhere in the graph the flux is maintained, i.e.,
every molecule is coming back to it's source node in a cycle.
%
The graph follows the fusion rules as discussed earlier and
is a 3-connected graph.
\ashu{R Q molecule types are not discussed anywhere.}
\end{example}

### 2017-07-14 paper/pm-1-matrix.tex
more text

\begin{figure}
\centering
\begin{minipage}{0.50\linewidth}
  \hspace{-4ex}
\begin{tikzpicture}
\matrix [matrix of math nodes,left delimiter=(,right delimiter=),row sep=0.16cm,column sep=0.1cm] (m) {
\times & \times & \times &\times&\times&\times & \times & \times\\
\times & \times & \times&\times&\times&\times& 1 &\times \\
\times & \times & \times&\times&\times&1&\times &\times\\
\times & \times & \times&\times & 1 & \times &\times & \times\\
 \times & \times & \times & \times & \times & \times & \times & \times\\
 \times & \times & \times &\times & \times & \times & \times & \times\\
 \times & \times & \times & \times & \times & \times & \times & \times\\
 \times & \times & \times & \times & \times & \times&\times & \times\\};

@@

\begin{pgfonlayer}{myback}

\foreach \element in {m-1-7,m-3-8,m-5-1,m-5-2,m-5-3,m-5-4,m-6-1,m-6-2,m-6-3,m-6-4,m-7-1,m-7-2,m-7-3,m-7-4,m-8-1,m-8-2,m-8-3,m-8-4}{
\highlight[pink]{\element}{\element}
}
\foreach \element in {m-2-7,m-3-6,m-4-5}{
\fhighlight[blue!10]{\element}{\element}
}
\end{pgfonlayer}

\end{tikzpicture}  
\end{minipage}
\begin{minipage}{0.45\linewidth}

\begin{tikzpicture}[node distance = 30mm]
  \node[draw] (n0) {$n_0:\overline{01234}$};
  \node[draw,below left of=n0] (n1) {$n_1:\overline{01236}$};
  \node[draw,below right of=n0] (n2) {$n_2:\overline{12357}$};

@@

\caption{\textbf{Pairing matrix}. VTS has 3 compartments and 8 molecules. Molecules are numbered 0-7 and and intersection matrix entry describes the fusion dependency. The entry 1 represents pairing, entry $\times$ represents no dependency and rectangles colored $\times$ one represents don't cares. In the right side of the pairing matrix is the graph VTS representation. Everwhere in the graph you can see the flux is maintained, that is every molecule is coming back to it's source node in a cycle. } \label{fig:M1}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\begin{minipage}{0.45\linewidth}

\begin{tikzpicture}[node distance = 26mm]
  \node[draw] (n0) {$n_0:\overline{01234}$};
  \node[draw,below left of=n0] (n1) {$n_1:\overline{01236}$};
  \node[draw,below right of=n0] (n2) {$n_2:\overline{12357}$};

\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.50\linewidth}
  \center
\begin{tikzpicture}
\matrix [matrix of math nodes,left delimiter=(,right delimiter=),
         row sep=0.07cm,column sep=0.07cm] (m) {
\times & \times & \times &\times&\times&\times & \times & \times\\
\times & \times & \times&\times&\times&\times& 1 &\times \\
\times & \times & \times&\times&\times&1&\times &\times\\
\times & \times & \times&\times & 1 & \times &\times & \times\\
 \times & \times & \times & \times & \times & \times & \times & \times\\
 \times & \times & \times &\times & \times & \times & \times & \times\\
 \times & \times & \times & \times & \times & \times & \times & \times\\
 \times & \times & \times & \times & \times & \times&\times & \times\\};

@@

% \begin{pgfonlayer}{myback}
% \foreach \element in {m-1-7,m-3-8,m-5-1,m-5-2,m-5-3,m-5-4,m-6-1,m-6-2,m-6-3,m-6-4,m-7-1,m-7-2,m-7-3,m-7-4,m-8-1,m-8-2,m-8-3,m-8-4}{
% \highlight[pink]{\element}{\element}
% }
% \foreach \element in {m-2-7,m-3-6,m-4-5}{
% \fhighlight[blue!10]{\element}{\element}
% }
% \end{pgfonlayer}

@@

\caption{An example of VTS and corresponding pairing matrix.} \label{fig:M1}
\end{figure}
